---
title: "CAMELS import exploration"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## CAMELS data

You get download a zip file with all the data. Once unzip on your local file system here is the file structure you get (only directories / folders)

```{bash file structure, eval=FALSE}
├── basin_set_full_res
├── basin_timeseries_v1p2_metForcing_obsFlow
│   ├── basin_dataset_public
│   │   └── basin_mean_forcing
│   │       ├── daymet
│   │       │   ├── 01
│   │       │   ├── 02
│   │       │   ├── 03
│   │       │   ├── 04
│   │       │   ├── 05
│   │       │   ├── 06
│   │       │   ├── 07
│   │       │   ├── 08
│   │       │   ├── 09
│   │       │   ├── 10
│   │       │   ├── 11
│   │       │   ├── 12
│   │       │   ├── 13
│   │       │   ├── 14
│   │       │   ├── 15
│   │       │   ├── 16
│   │       │   ├── 17
│   │       │   └── 18
│   │       ├── maurer
│   │       │   ├── 01
│   │       │   ├── 02
│   │       │   ├── 03
│   │       │   ├── 04
│   │       │   ├── 05
│   │       │   ├── 06
│   │       │   ├── 07
│   │       │   ├── 08
│   │       │   ├── 09
│   │       │   ├── 10
│   │       │   ├── 11
│   │       │   ├── 12
│   │       │   ├── 13
│   │       │   ├── 14
│   │       │   ├── 15
│   │       │   ├── 16
│   │       │   ├── 17
│   │       │   └── 18
│   │       ├── nldas
│   │       │   ├── 01
│   │       │   ├── 02
│   │       │   ├── 03
│   │       │   ├── 04
│   │       │   ├── 05
│   │       │   ├── 06
│   │       │   ├── 07
│   │       │   ├── 08
│   │       │   ├── 09
│   │       │   ├── 10
│   │       │   ├── 11
│   │       │   ├── 12
│   │       │   ├── 13
│   │       │   ├── 14
│   │       │   ├── 15
│   │       │   ├── 16
│   │       │   ├── 17
│   │       │   └── 18
│   │       └── v1p15
│   │           ├── daymet
│   │           │   ├── 01
│   │           │   ├── 02
│   │           │   ├── 03
│   │           │   ├── 04
│   │           │   ├── 05
│   │           │   ├── 06
│   │           │   ├── 07
│   │           │   ├── 08
│   │           │   ├── 09
│   │           │   ├── 10
│   │           │   ├── 11
│   │           │   ├── 12
│   │           │   ├── 13
│   │           │   ├── 14
│   │           │   ├── 15
│   │           │   ├── 16
│   │           │   ├── 17
│   │           │   └── 18
│   │           └── nldas
│   │               ├── 01
│   │               ├── 02
│   │               ├── 03
│   │               ├── 04
│   │               ├── 05
│   │               ├── 06
│   │               ├── 07
│   │               ├── 08
│   │               ├── 09
│   │               ├── 10
│   │               ├── 11
│   │               ├── 12
│   │               ├── 13
│   │               ├── 14
│   │               ├── 15
│   │               ├── 16
│   │               ├── 17
│   │               └── 18
│   └── basin_dataset_public_v1p2
│       ├── basin_mean_forcing
│       │   ├── daymet
│       │   │   ├── 01
│       │   │   ├── 02
│       │   │   ├── 03
│       │   │   ├── 04
│       │   │   ├── 05
│       │   │   ├── 06
│       │   │   ├── 07
│       │   │   ├── 08
│       │   │   ├── 09
│       │   │   ├── 10
│       │   │   ├── 11
│       │   │   ├── 12
│       │   │   ├── 13
│       │   │   ├── 14
│       │   │   ├── 15
│       │   │   ├── 16
│       │   │   ├── 17
│       │   │   └── 18
│       │   ├── maurer
│       │   │   ├── 01
│       │   │   ├── 02
│       │   │   ├── 03
│       │   │   ├── 04
│       │   │   ├── 05
│       │   │   ├── 06
│       │   │   ├── 07
│       │   │   ├── 08
│       │   │   ├── 09
│       │   │   ├── 10
│       │   │   ├── 11
│       │   │   ├── 12
│       │   │   ├── 13
│       │   │   ├── 14
│       │   │   ├── 15
│       │   │   ├── 16
│       │   │   ├── 17
│       │   │   └── 18
│       │   └── nldas
│       │       ├── 01
│       │       ├── 02
│       │       ├── 03
│       │       ├── 04
│       │       ├── 05
│       │       ├── 06
│       │       ├── 07
│       │       ├── 08
│       │       ├── 09
│       │       ├── 10
│       │       ├── 11
│       │       ├── 12
│       │       ├── 13
│       │       ├── 14
│       │       ├── 15
│       │       ├── 16
│       │       ├── 17
│       │       └── 18
│       ├── basin_metadata
│       ├── elev_bands_forcing
│       │   └── daymet
│       │       ├── 01
│       │       ├── 02
│       │       ├── 03
│       │       ├── 04
│       │       ├── 05
│       │       ├── 06
│       │       ├── 07
│       │       ├── 08
│       │       ├── 09
│       │       ├── 10
│       │       ├── 11
│       │       ├── 12
│       │       ├── 13
│       │       ├── 14
│       │       ├── 15
│       │       ├── 16
│       │       ├── 17
│       │       └── 18
│       ├── hru_forcing
│       │   └── daymet
│       │       ├── 01
│       │       ├── 02
│       │       ├── 03
│       │       ├── 04
│       │       ├── 05
│       │       ├── 06
│       │       ├── 07
│       │       ├── 08
│       │       ├── 09
│       │       ├── 10
│       │       ├── 11
│       │       ├── 12
│       │       ├── 13
│       │       ├── 14
│       │       ├── 15
│       │       ├── 16
│       │       ├── 17
│       │       └── 18
│       ├── shapefiles
│       │   ├── Region_01_contours_simplify_100
│       │   ├── Region_01_nhru_simplify_100
│       │   └── merge
│       └── usgs_streamflow
│           ├── 01
│           ├── 02
│           ├── 03
│           ├── 04
│           ├── 05
│           ├── 06
│           ├── 07
│           ├── 08
│           ├── 09
│           ├── 10
│           ├── 11
│           ├── 12
│           ├── 13
│           ├── 14
│           ├── 15
│           ├── 16
│           ├── 17
│           └── 18
└── camels_attributes_v2.0
```

### Basin mean forcing -- Daymet

the files have a header of 3 lines and are not recognized as tab delimited by `readr`, so using white spaces for now. Within the daymet directory `basin_timeseries_v1p2_metForcing_obsFlow/basin_dataset_public_v1p2/basin_mean_forcing/daymet`, files are organized according to USGS Hydrological Units classification ([HUC](https://water.usgs.gov/GIS/huc.html)) with HUC2 as subdirectories. The filenaming convention uses the HUC8 gauge ID +`_lump_cida_forcing_leap.txt`

```{r import one file}
library(readr)
library(stringr)
library(fs)

# Constant
main_dir <- "~/Data/CAMELS"
ts_dir <- "basin_timeseries_v1p2_metForcing_obsFlow/basin_dataset_public_v1p2"
daymet_dir <- "basin_mean_forcing/daymet"

# To become a variable
huc8 <- "01013500"
huc2 <- str_extract(huc8, "^.{2}")


# read the file in
test_file <- read_table2(
  file.path(main_dir, ts_dir, daymet_dir, huc2, paste0(huc8,"_lump_cida_forcing_leap.txt")), 
  skip = 3)
```
Note: the last year of information is 2014.

### Get the attribute

Since we need to get the gauge id from a bunch of text files, grep since to be the fastes way to achieve this. Need to check how it will work on Windows machines.

```{r}
text_blurb <- system2("grep", c(huc8, '~/Data/CAMELS/camels_attributes_v2.0/*'), stdout = TRUE)
as.data.frame(text_blurb)
```


Get all the CAMELS attribute files

```{r}
att_files <- list.files(file.path(main_dir,"camels_attributes_v2.0"),
                        pattern = "^camels_[^a]", # remove the xls too; will be better with the extension instead
                        full.names = TRUE)
```

Since each table is structured differently, we are going to store them in a named list




```{r}
att_list <- map(local_datasets, read_d1_files) %>% 
  set_names(map(., ~.x$summary_metadata$value[.x$summary_metadata$name == "File_Name"]))
```

